Spatial evolution of solar wind discontinuities in the outer heliosphere

### 2024-11-10 article.qmd
update manuscript

In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) [@boltonJunoMission2017]. The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin. Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously. This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]. Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].

@@

@@

The solar wind plasma state, as evidenced by the sunspot number (referenced in @fig-overview), plays a crucial role in understanding the dynamics of discontinuities. During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity. However, by the end of the mission's cruise phase, there was a significant decline in solar activity. This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.

Datasets collected from missions such as STEREO, ARTEMIS, and WIND will complement observations from Juno, offering a broader contextual perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020]. The table below summarizes the time resolution of magnetic field and plasma data for PSP, Juno, Wind, ARTEMIS, and STEREO.

@@

However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models. Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location. This model, which utilizes the BATSRUS MHD solver, simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study. The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model. The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.

@@

$$
B_m(t) = B_{m0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c
$${#eq-fit}

where $B_{m0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c$ should theoretically be zero. However, in the context of data processing, incorporating $c$ can enhance the fitting accuracy).

>>>>

In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft [@boltonJunoMission2017] during its cruise phases (2011-2016), with its orbits shown in panel (a) of @fig-fig-overview. The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin. Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously. This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]. Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].

@@

The solar wind plasma state, as evidenced by the sunspot number (referenced in panel (c) of @fig-overview), plays a crucial role in understanding the dynamics of discontinuities. During the initial phase of the JUNO mission, the sunspot number reached its peak, indicating a period of heightened solar activity. However, by the end of the mission's cruise phase, there was a significant decline in solar activity. This variation underscores the importance of calibrating the discontinuity properties in relation to solar activity levels to account for temporal fluctuations.

@@

Datasets collected from missions such as STEREO, ARTEMIS, and WIND will complement observations from Juno, offering a broader contextual perspective on heliospheric conditions and enabling a multi-point analysis of discontinuity properties [@velliUnderstandingOriginsHeliosphere2020]. The table below summarizes the time resolution of magnetic field and plasma data for Juno, Wind, ARTEMIS, and STEREO.

@@

However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models. Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location. This model, which utilizes the BATSRUS MHD solver[@tothAdaptiveNumericalAlgorithms2012], simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study. The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model. The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.

@@

$$
B_l(t) = B_{l0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c_l
$${#eq-fit}

where $B_{l0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c_l$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c_l$ should theoretically be zero. However, in the context of data processing, incorporating $c_l$ can enhance the fitting accuracy).
